---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "Serena Theobald"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```
```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_boxplot()
```

1. Write code for a plot and describe what you observe?

The code filters the data to only include rows from Massachusetts, then creates a box plot visualization where the x-axis represents dates, the y-axis represents case counts, and different races are represented by different colors. This helps us understand the distribution of COVID-19 cases across different racial groups over time in Massachusetts.

2. Are there any conclusions you can draw?

Between October and January, there are wider box plots, which indicates a more varied number of cases. Between July and October, there are narrower box plots, which indicate more consistency in the number of cases reported.

3. What were you not able to do due to not having the R knowledge?

Because I don't have the R knowledge yet, creating advanced visualizations using packages like ggplot2 is a bit challenging. Although I created a boxplot, there are probably a lot of other types of plots and customization options that reveal more intricate details in the COVID data.

4. What other data would be useful to better understand this data?

To better understand the data in the context of COVID-19 cases in Massachusetts differentiated by race over time, it might be good to have vaccination data (vaccination rates and vaccine distribution), demographic data, socioeconomic data, and policy intervention data for that specific state.
